---
title: "Examination of College Endowments"
author: "Christopher T. Davidson, Ph.D."
date: "August 4, 2021"
output:
  word_document: default
---
# Executive Summary 

# Introduction
TALK OF Endowments


## The Integrated Postsecondary Education Data System  Data 
The Department of Education collects data annually through a series of interrelated surveys that all institutions--college, university, technical, and vocational--that participate in federal Title IV financial aid programs established by the Higher Education Act of 1965. Annually, more than 7,500 institutions ranging from research universities, state colleges, private religious and liberal arts institutions, for-profit schools, community and technical colleges, and non-degree-granting institutions complete the surveys for [Integrated Postsecondary Education Data System](https://nces.ed.gov/ipeds/) (IPEDS). 

Data collected from institutions include information in eight areas: 

* Institutional Characteristics;
* Institutional Prices;
* Admissions;
* Enrollment;
* Student Financial Aid;
* Degrees and Certificates Conferred; 
* Student Persistence and Success; and,
* Academic Libraries, Institutional, and Human Fiscal Resources.

## Purpose Statement 
As one of the definitive sources for information about postsecondary education in the United States, IPEDS is used by Congress, federal and state government agencies, education leaders and researchers, private businesses, and the media for various purposes. The purpose of this project was to examine trends in four-year college endowments at public and private institutions. Additionally, I sought to develop and train a series of machine learning algorithms to predict college endowment values reported in IPEDS while maximizing the accuracy of the algorithm.

The Root Mean Square Error (RMSE) served as the value to evaluate the accuracy of each model. The RMSE is a standard way to measure the error between predicted and true values in a model. A smaller RMSE is interpreted as the model being more accurate than a larger RMSE.^[Rafael A. Irizarry. (2020). Introduction to Data Science: Data Analysis and Prediction Algorithms with R (1st ed.). Taylor & Francis Group.] 

This report provides a description of the methods used to download and clean the data, data set using descriptive statistics, the methods to conduct an initial exploratory data analysis of the training subset of data before creating a series of machine learning algorithms. The report will then provide the results and offer a discussion of the analysis before providing concluding remarks. 

## Research Questions
This study examined X research questions:
1. Research 1
2. Research 2
3. Research 3

# Methods & Analysis

## College Endowment Dataset from IPEDS 
The data for this analysis came from IPEDS. The code to build the college data set was written to merge 18 separate data files to create the College Graduation Data set that included 10-years of data to account for any anomalies in the data for 2,479 four-year public and private institutions. The 19th file provides the definitions of the variables in the data set.  

Once the files were merged, there were 24,790 observations for 15 variables. Any cases that had at least one null value for any variable were removed from the data set leaving 13,785 observations. Table 1 provides the definitions for the included variables from [IPEDS](https://nces.ed.gov/ipeds/).

```{r Create Dataset & Variables Table, echo=FALSE, message=FALSE, warning=FALSE}
## Install Libraries ##
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(flextable)) install.packages("flextable", repos = "http://cran.us.r-project.org")
if(!require(gtsummary)) install.packages("gtsummary", repos = "http://cran.us.r-project.org")
if(!require(Rcpp)) install.packages("Rcpp", repos = "http://cran.us.r-project.org")
if(!require(formattable)) install.packages("formattable", repos = "http://cran.us.r-project.org")
if(!require(gt)) install.packages("gt", repos = "http://cran.us.r-project.org")


if(!require(broom)) install.packages("broom", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table)) install.packages("data.table", repos = "http://cran.us.r-project.org")
if(!require(ggplot2)) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
if(!require(rpart)) install.packages("rpart", repos = "http://cran.us.r-project.org")
if(!require(rattle)) install.packages("rattle", repos = "http://cran.us.r-project.org")
if(!require(randomForest)) install.packages("randomForest", repos = "http://cran.us.r-project.org")
if(!require(rpart.plot)) install.packages("rpart.plot", repos = "http://cran.us.r-project.org")

#Load Data Files
EndowFASB <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/EndowmentFASB.csv")
EndowGASB <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/EndowmentGASB.csv")
FTE <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/FTE.csv")
GRAD <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/GraduationRate.csv")
U_Headcount <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/Headcount.csv")
HighDegree <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/HighestDegree.csv")
HighDegreeValue <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/HighestDegreeValues.csv")
INST_Control <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_Control.csv")
INST_ControlValue <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_ControlValues.csv")
Retention <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/Retention.csv")
Tuition_In <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/In-State_Tuition.csv")
Tuition_Out <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/Out-of-State_Tuition.csv")
INST_Level <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_Level.csv")
INST_LevelValues <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_LevelValue.csv")
StateAbbr <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/StateAbbr.csv")
StateAbbrLabels <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/StateAbbrValues.csv")
INSTsize <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_Size.csv")
INSTsizeLabels<- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/INST_SizeValues.csv")
Variables <- read.csv("https://raw.githubusercontent.com/drcdavidson/college-endowments/main/IPEDS_Data/Variables.csv")

###################################################
## Clean Data and Combine Files into the Dataset ##
names(INST_Level) <- c("UnitID", "INST", "INST_Level_Code")
names(INST_LevelValues) <- c("Variable", "INST_Level_Code", "INST_Level")

Colleges <- INST_Level %>% left_join(INST_LevelValues, by = 'INST_Level_Code')   #Join INST Levels with Values
Colleges <- select(Colleges, -3,-4)   #Remove unneeded columns
rm(INST_Level, INST_LevelValues)  #Remove merged datasets 

##Add Public & Private Control to Colleges
names(INST_ControlValue) <- c("Variable","INST_Control","Sector") #edit column names for join
INST_Control <- INST_Control %>% left_join(INST_ControlValue, by = 'INST_Control') #join tables
rm(INST_ControlValue) #remove data table
Colleges <- Colleges %>% left_join(INST_Control, by = 'UnitID') #add sectors to Colleges table
Colleges <- Colleges[-c(5:6)]  # remove unneeded columns
rm(INST_Control)  #remove table

##Add Highest Degree
names(HighDegreeValue) <- c("Variable","HighestDegree","Highest_Degree")
HighDegree <- HighDegree %>% left_join(HighDegreeValue, by = 'HighestDegree')
rm(HighDegreeValue)
Colleges <- Colleges %>% left_join(HighDegree, by ='UnitID')
Colleges <- Colleges[-c(4,6:8)]
rm(HighDegree)

##Add INSTsize
INSTsize <- INSTsize %>% left_join(INSTsizeLabels, by = 'INST_Size_Value')
rm(INSTsizeLabels)
Colleges <- Colleges %>% left_join(INSTsize, by = 'UnitID')
Colleges <- Colleges[-6]
rm(INSTsize)

##Add StateAbbr
Colleges <- Colleges %>% left_join(StateAbbr, by = 'UnitID') %>%
  left_join(StateAbbrLabels, by = 'State_Abbr')
Colleges <- Colleges[-7]
rm(StateAbbr, StateAbbrLabels)

##########
## Clean EndowGASB
EndowG <- EndowGASB
names(EndowG) <- c("UnitID", 2019:2010)
EndowGASB <- EndowG %>% select(UnitID) %>% mutate(Year=2019, EndowmentG = EndowG$`2019`) #create subset of rates

EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2018,"EndowmentG" = EndowG$`2018`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2017,"EndowmentG" = EndowG$`2017`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2016,"EndowmentG" = EndowG$`2016`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2015,"EndowmentG" = EndowG$`2015`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2014,"EndowmentG" = EndowG$`2014`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2013,"EndowmentG" = EndowG$`2013`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2012,"EndowmentG" = EndowG$`2012`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2011,"EndowmentG" = EndowG$`2011`))
EndowGASB <- bind_rows(EndowGASB, data.frame("UnitID" = EndowG$UnitID,"Year" = 2010,"EndowmentG" = EndowG$`2010`))

## Clean EndowFASB
EndowF <- EndowFASB
names(EndowF) <- c("UnitID", 2019:2010)
EndowFASB <- EndowF %>% select(UnitID) %>% mutate(Year=2019, EndowmentF = EndowF$`2019`) #create subset of rates

#Bind rows into a tidy format
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2018,"EndowmentF" = EndowF$`2018`))
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2017,"EndowmentF" = EndowF$`2017`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2016,"EndowmentF" = EndowF$`2016`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2015,"EndowmentF" = EndowF$`2015`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2014,"EndowmentF" = EndowF$`2014`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2013,"EndowmentF" = EndowF$`2013`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2012,"EndowmentF" = EndowF$`2012`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2011,"EndowmentF" = EndowF$`2011`)) 
EndowFASB <- bind_rows(EndowFASB, data.frame("UnitID" = EndowF$UnitID,"Year" = 2010,"EndowmentF" = EndowF$`2010`))

#Remove Data
rm(EndowF, EndowG)

Endowment <- EndowFASB %>% cbind("EndowmentG" = EndowGASB$EndowmentG)

#Create Combined Endowment 
Endowment <- Endowment %>% 
  mutate(Endowment = ifelse(UnitID == EndowGASB$UnitID & Year == EndowGASB$Year & 
                              is.na(EndowGASB$EndowmentG), EndowmentF, EndowGASB$EndowmentG))

#Remove Unneeded Data
rm(EndowFASB,EndowGASB)
Endowment <- Endowment[-c(3:4)]

#Add Endowment to Colleges & Remove unneeded data file
Colleges <- Colleges %>% right_join(Endowment, by = 'UnitID')
rm(Endowment)

##########
##Clean In-State Tuition
names(Tuition_In) <- c("UnitID", "InstName", 2020:2011) #rename columns 
InState <- Tuition_In %>% select(UnitID) %>% mutate(Year = 2020, "In" = Tuition_In$`2020`)   #create subset of rates

#Bind rows into a tidy format 
InState <- bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID,"Year" = 2019,"In" = Tuition_In$`2019`))
InState <- bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2018, "In" = Tuition_In$`2018`)) 
InState <- bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2017, "In" = Tuition_In$`2017`)) 
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2016, "In" = Tuition_In$`2016`)) 
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2015, "In" = Tuition_In$`2015`))
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2014, "In" = Tuition_In$`2014`)) 
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2013, "In" = Tuition_In$`2013`))
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2012, "In" = Tuition_In$`2012`)) 
InState <-  bind_rows(InState, data.frame("UnitID" = Tuition_In$UnitID, "Year" = 2011, "In" = Tuition_In$`2011`))

#Rename column
names(InState)[3]<-"InState"

#Remove Data
rm(Tuition_In)

#Add to Colleges Dataset
Colleges <- left_join(Colleges,InState,by=c('UnitID','Year'))

#Remove unneeded data file
rm(InState)

##########
##Clean Out-of-State Tuition
names(Tuition_Out) <- c("UnitID", "InstName", 2020:2011) #rename columns 
OutState <- Tuition_Out %>% select(UnitID) %>% mutate(Year = 2020, "Out" = Tuition_Out$`2020`)   #create subset of rates

#Bind rows into a tidy format 
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2019, "Out" = Tuition_Out$`2019`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2018, "Out" = Tuition_Out$`2018`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2017, "Out" = Tuition_Out$`2017`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2016, "Out" = Tuition_Out$`2016`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2015, "Out" = Tuition_Out$`2015`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2014, "Out" = Tuition_Out$`2014`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2013, "Out" = Tuition_Out$`2013`))
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2012, "Out" = Tuition_Out$`2012`)) 
OutState <- bind_rows(OutState, data.frame("UnitID" = Tuition_Out$UnitID, "Year" = 2011, "Out" = Tuition_Out$`2011`))

#Rename column
names(OutState)[3]<-"OutState"

#Remove Data
rm(Tuition_Out)

#Add to Colleges Data
Colleges <- Colleges %>% left_join(OutState, by = c('UnitID','Year'))
rm(OutState)

###############
##Clean Retention
names(Retention) <- c("UnitID", 2019:2010)
Fall_Ret <- Retention %>% select(UnitID) %>% mutate(Year = 2019, Retention = Retention$`2019`)  #create subset of rates

#Bind rows into a tidy format 
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2018,"Retention" = Retention$`2018`)) 
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2017,"Retention" = Retention$`2017`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2016,"Retention" = Retention$`2016`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2015,"Retention" = Retention$`2015`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2014,"Retention" = Retention$`2014`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2013,"Retention" = Retention$`2013`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2012,"Retention" = Retention$`2012`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2011,"Retention" = Retention$`2011`))
Fall_Ret <- bind_rows(Fall_Ret, data.frame("UnitID" = Retention$UnitID,"Year" = 2010,"Retention" = Retention$`2010`))

#Remove Data
rm(Retention)

#Add to Colleges Data & Remove data file
Colleges <- Colleges %>% left_join(Fall_Ret, by = c('UnitID','Year'))
rm(Fall_Ret)

########## 
## Clean Headcount
names(U_Headcount) <- c("UnitID", 2019:2010)
Headcount <- U_Headcount %>% select(UnitID) %>% mutate(Year=2019, Headcount = U_Headcount$`2019`) #create subset of rates

#Bind rows into a tidy format 
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2018,"Headcount" = U_Headcount$`2018`))
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2017,"Headcount" = U_Headcount$`2017`))
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2016,"Headcount" = U_Headcount$`2016`)) 
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2015,"Headcount" = U_Headcount$`2015`)) 
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2014,"Headcount" = U_Headcount$`2014`)) 
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2013,"Headcount" = U_Headcount$`2013`)) 
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2012,"Headcount" = U_Headcount$`2012`))
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2011,"Headcount" = U_Headcount$`2011`))
Headcount <- bind_rows(Headcount, data.frame("UnitID" = U_Headcount$UnitID,"Year" = 2010,"Headcount" = U_Headcount$`2010`))

#Remove Data
rm(U_Headcount)

#Add to Colleges Data & Remove data file
Colleges <- Colleges %>% left_join(Headcount, by = c('UnitID','Year'))
rm(Headcount)

###############
##Clean FTE
names(FTE) <- c("UnitID","Name",2019:2010)
FullTimeE <- FTE
FTE <- FullTimeE %>% select(UnitID) %>% mutate(Year=2019, FTE=FullTimeE$`2019`)     #create subset of rates

#Bind rows into a tidy format 
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2018,"FTE" = FullTimeE$`2018`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2017,"FTE" = FullTimeE$`2017`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2016,"FTE" = FullTimeE$`2016`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2015,"FTE" = FullTimeE$`2015`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2014,"FTE" = FullTimeE$`2014`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2013,"FTE" = FullTimeE$`2013`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2012,"FTE" = FullTimeE$`2012`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2011,"FTE" = FullTimeE$`2011`))
FTE <- bind_rows(FTE, data.frame("UnitID" = FullTimeE$UnitID,"Year" = 2010,"FTE" = FullTimeE$`2010`))
  
#Remove Data
rm(FullTimeE)

#Add to Colleges Data & Remove data file
Colleges <- Colleges %>% left_join(FTE, by = c('UnitID','Year'))
rm(FTE)

###############
## Clean Grad
Graduate <- GRAD
names(Graduate) <- c("UnitID", 2019:2010)
GRAD <- Graduate %>% select(UnitID) %>% mutate(Year=2019, GRAD=Graduate$`2019`)   #create subset of rates

#Bind rows into a tidy format
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2018,"GRAD" = Graduate$`2018`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2017,"GRAD" = Graduate$`2017`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2016,"GRAD" = Graduate$`2016`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2015,"GRAD" = Graduate$`2015`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2014,"GRAD" = Graduate$`2014`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2013,"GRAD" = Graduate$`2013`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2012,"GRAD" = Graduate$`2012`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2011,"GRAD" = Graduate$`2011`)) 
GRAD <- bind_rows(GRAD, data.frame("UnitID" = Graduate$UnitID,"Year" = 2010,"GRAD" = Graduate$`2010`))

#Remove Data
rm(Graduate)

#Add to Colleges Data & Remove data file
Colleges <- Colleges %>% left_join(GRAD, by = c('UnitID','Year'))
rm(GRAD)

# Reorder Columns & Rename FINAL DataSet
Colleges <- Colleges[,c(1:5,7,6,8:15)]

#Remove cases with at least one null value
Colleges <- Colleges[complete.cases(Colleges),]

#####################################################################
#Create data.frame with variables and definitions
flextable(Variables) %>% 
  set_table_properties(width = .75, layout = "autofit") %>%
  set_caption(caption = " IPEDS Definitions for Variables") %>%
  footnote(i=1, j=2, 
           value= as_paragraph("Some definitions were modified for gramatical purposes."),
           ref_symbols = "a",
           part = "header") %>%
  theme_vanilla()
```

All of the institutions in the dataset are classified as *four-or more years*. The data set has nearly twice as many *Private not-for-profit* (N = 9,901) than *Public* (N = 4,694) sector institutions of higher education. The highest degree offered from the colleges included in the data set were *Bachelor's Degree* (N = 1,969) and *Master's Degree* (N = 4,670). and *Doctor's Degrees* are split between Professional Practice (N = 1,554), Research/Scholarship (N = 1,908), Research/Scholarship and Professional Practice (N = 3,413), and Other (271) degrees. Institution sizes ranged from Under 1,000 (N = 2,531) to 20,000 and above (N = 1,291). Most institutions in the data fall between 1,000-4,999 students (N = 6,454). Table 2 provides the descriptive statistics for the categorical variables. 

```{r Create Categorical Descriptives, echo=FALSE, message=FALSE, warning=FALSE}
#####################################################################
## Descriptives of College Dataset
#Categorical Variables 
t1 <- Colleges %>%
  select("INST_Level","Sector","Highest_Degree","INST_Size") %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_categorical() ~ "{n}"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**",
                     stat_0 ~ "**N**")) %>%
  modify_footnote(list(stat_0 ~ NA))

#Export to Flextable
College_Categ <- as_flex_table(t1, include = everything(), return_calls = FALSE,
                              strip_md_bold = TRUE) 

College_Categ %>%
  set_table_properties(width = .75, layout = "autofit") %>%
  set_caption(caption = " Frequencies for Categorical Variables") %>%
  theme_vanilla()

#Remove unneeded table
rm(t1)
```

The mean endowment is \$315,043,226 with a range of \$1 to \$40,929,700,000. The mean in-state tuition is \$21,560 and mean out-of-state tuition is $25,159. The range for both in-state and out-of-state tuitition rates is \$0 to \$59,430. The mean retention rate is 75% and a range of 0 to 100%. The mean unduplicated headcount enrollment is 8,227 students and a range from 17 to 167,841 students. The mean full-time equivalent enrollment is 6,292 with a range from 10 to 84,219 fte. The mean graduation rate is 53% and ranged from 0% to 100%. Table 3 provides the descriptive statistics for the continuous variables. 

```{r Continuous Descriptives, echo=FALSE, message=FALSE, warning=FALSE}
################
# Continuous Variables
t1 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD") %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**",stat_0 ~ "**Mean (SD)**")) %>%
  modify_footnote(list(stat_0 ~ NA))

t2 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD")  %>%
  tbl_summary(by = NULL, label = NULL,
              statistic = list(all_continuous() ~ "{min}"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**",stat_0 ~ "**Minimum**")) %>%
  modify_footnote(list(stat_0 ~ NA))

t3 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD")  %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_continuous() ~ "{max}"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**", stat_0 ~ "**Maximum**")) %>%
  modify_footnote(list(stat_0 ~ NA))

t4 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD")  %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_continuous() ~ "{median}"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**",stat_0 ~ "**Median**")) %>%
  modify_footnote(list(stat_0 ~ NA)) 

t5 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD") %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_continuous() ~ "{p25}"),
              missing = "no") %>%
  modify_header(list(label ~ "**Variable**", stat_0 ~ "**IQR Lower**")) %>%
  modify_footnote(list(stat_0 ~ NA)) 

t6 <- Colleges %>%
  select("Endowment","InState","OutState","Retention","Headcount","FTE","GRAD")  %>%
  tbl_summary(by = NULL, label = NULL, 
              statistic = list(all_continuous() ~ "{p75}"),
              missing = "no") %>% 
  modify_header(list(label ~ "**Variable**",stat_0 ~ "**IQR Upper**")) %>%
  modify_footnote(list(stat_0 ~ NA)) 

Col_Desc <- tbl_merge(list(t1,t2,t3,t4,t5,t6)) %>%
  modify_spanning_header(everything() ~ NA_character_)

# Remove Unneeded Values & Tables
rm(t1,t2,t3,t4,t5,t6)

#Export to Flextable
College_Desc <- as_flex_table(Col_Desc, include = everything() , return_calls = FALSE,
                              strip_md_bold = TRUE)
College_Desc <- College_Desc %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  set_caption(caption = " Descriptive Statistics for Continuous Variables") %>%
  theme_vanilla()

# Remove Uneeded Table
rm(Col_Desc)
```

In addition to the descriptive information, Tables 4, 5, and 6 provide the Top 10 Endowments for all institutions, private not-for-profit institutions, and public institutions respectively.

```{r Top 10 Endowments, echo=FALSE, message=FALSE, warning=FALSE}
######################################################################
#Top 10 Endowments 
#Subset data into one year 
FinalYr <- filter(Colleges, Year == 2019)

#Arrange data from largest to smallest Endowment
Top <- arrange(FinalYr,desc(Endowment)) %>% select(INST, Sector, Endowment) 

#Get Top 10 Endowments
Top10 <- head(Top,10)

#Convert Endowment to currency 
Top10 <- gt(Top10)
Top10 <- fmt_currency(Top10, "Endowment", currency = "USD",sep_mark = ",") %>%
  as.data.frame()

#Final Table for presentation
flextable(Top10) %>% 
  set_table_properties(width = .75, layout = "autofit") %>%
  set_caption(caption = " Top 10 Highest Endowments - All Institutions") %>%
  theme_vanilla()

#Get Top 10 Private Endowments 
Top10_Pri <- Top %>% filter(Sector == 'Private not-for-profit')
Top10_Pri <- head(Top10_Pri,10)
Top10_Pri <- gt(Top10_Pri)
Top10_Pri <- fmt_currency(Top10_Pri, "Endowment", currency = "USD",sep_mark = ",") %>%
  as.data.frame()

flextable(Top10_Pri) %>% 
  set_table_properties(width = .75, layout = "autofit") %>%
  set_caption(caption = " Top 10 Highest Endowments - Private Non-for-Profit Institutions") %>%
  theme_vanilla()

#Get Top 10 Public Endowments 
Top10_Pub <- Top %>% filter(Sector == 'Public')
Top10_Pub <- head(Top10_Pub,10)
Top10_Pub <- gt(Top10_Pub)
Top10_Pub <- fmt_currency(Top10_Pub, "Endowment", currency = "USD",sep_mark = ",") %>%
  as.data.frame()

flextable(Top10_Pub) %>% 
  set_table_properties(width = .75, layout = "autofit") %>%
  set_caption(caption = " Top 10 Highest Endowments - Public Institutions") %>%
  theme_vanilla()

```

After removing cases with null values, eighty percent of the data set was split into the training data set used for tuning and 20% split into a test data set. The code also removed unneeded files from the working directory and environment.
